---
title: "People"
description: |
  Rutgers Applied Phonetics Group 
site: distill::distill_website
---


## Current members

<!-- Portfolio Gallery Grid -->
<!-- all images 225 x 300 --> 



```{r, echo=F, results='asis'}
library("glue")
library("fs")
library("here")
library("dplyr")
library("tibble")
library("stringr")

members <- tribble(
  ~'Name', ~'Role', ~'Email', ~'Website', ~'img', 
  "Joseph V. Casillas", "PI", "joseph.casillas@rutgers.edu", "https://www.jvcasillas.com", "jvc.png",
  "Laura Fernández Arroyo", "PhD student", "lf402@spanport.rutgers.edu", "https://laurafdeza.github.io", "lfa.png",
  "Juan José Garrido Pozú", "PhD student", "jjg280@scarletmail.rutgers.edu", " ", "jjgp.jpeg",
  "Kyle Parrish", "PhD student", "kcp74@scarletmail.rutgers.edu", " ", "kp.jpeg", 
  "Gabriela Constantin-Dureci", "PhD student", "gabriela.constantin.dureci@rutgers.edu", " ", "gcd.jpeg", 
  "Jiawei Shao", "PhD student", "js2845@scarletmail.rutgers.edu", " ", "jis.jpeg", 
  "Iván Andreu Rascón", "PhD student", "ia308@connect.rutgers.edu", " ", "ira.jpeg", 
  "Isabelle Chang", "Research assistant", "isc22@scarletmail.rutgers.edu", " ", "schwa.png", 
  "Katherine Taveras", "Research assistant", "kgtaveras@gmail.com", " ", "schwa.png", 
  ) 

cat('<div class="row">\n <div class="column">')
glue(
'
<div class="content">
 <div class="zoom">
 <center>
 <a href="{members$Website}">
 <img src="./images/members/{members$img}" alt="member" style="width:30%">
 </a>\n
 <small_text>[{members$Name}](mailto:{members$Email}), {members$Role}</small_text>\n
 </center>
 </div>
</div>
'
)
cat(' </div>\n</div>')
```






## Former members

- Avery Field (Aresty, Montclair State)
- Jack Fastenau (Lab assistant, New Jersey Medical School)
- Kimberly Gómez (Aresty lab assistant)

## Collaborators

- Dr. Miquel Simonet (University of Arizona)
- Dr. Nicole Rodríguez (Post-doc, Adam Mickiewicz University, Poznań, Poland)




## Directory

```{r, members, echo=F, layout="l-body-outset"}
members %>% 
  select(-img) %>% 
  knitr::kable()
```




<style type="text/css">

small_text {
  font-size: .85em;
}

* {
  box-sizing: border-box;
}

body {
  background-color: #fff;
}

.row {
  margin: 8px -16px;
}

/* Add padding BETWEEN each column (if you want) */
.row,
.row > .column {
  padding: 8px;
}

/* Create four equal columns that floats next to each other */
.column {
  float: left;
  width: 100%;
}

/* Clear floats after rows */ 
.row:after {
  content: "";
  display: table;
  clear: both;
}

/* Content */
.content {
  background-color: white;
  padding: 10px;
}

/* Responsive layout - makes a two column-layout instead of four columns */
@media screen and (max-width: 900px) {
  .column {
    width: 70%;
  }
}

/* Responsive layout - makes the two columns stack on top of each other instead of next to each other */
@media screen and (max-width: 600px) {
  .column {
    width: 90%;
  }
}

</style>

