---
title: "People"
description: |
  Rutgers Applied Phonetics Group 
site: distill::distill_website
---


## Current members

<!-- Portfolio Gallery Grid -->
<!-- all images 225 x 300 --> 



```{r, echo=F, results='asis'}
library("glue")
library("fs")
library("here")
library("dplyr")
library("tibble")
library("stringr")

members <- tribble(
  ~'current', ~'Name', ~'Role', ~'Email', ~'Website', ~'img', 
  1, "Joseph V. Casillas", "PI", "joseph.casillas@rutgers.edu", "https://www.jvcasillas.com", "jvc2022.png",
  0, "Laura Fernández Arroyo", "PhD student", "lf402@spanport.rutgers.edu", "https://www.laurafdeza.com/", "lfa.png",
  0, "Juan José Garrido Pozú", "Professor", "jjg280@scarletmail.rutgers.edu", "https://juanjgarridop.github.io", "jjgp.png",
  0, "Kyle Parrish", "Post-doc", "kcp74@scarletmail.rutgers.edu", "https://kparrish92.github.io", "kp.png", 
  1, "Gabriela Constantin-Dureci", "PhD student", "gabriela.constantin.dureci@rutgers.edu", "https://constantindureci.wixsite.com/profile", "gcd.png", 
  1, "Jiawei Shao", "PhD student", "js2845@scarletmail.rutgers.edu", " ", "jis.png", 
  1, "Iván Andreu Rascón", "PhD student", "ia308@connect.rutgers.edu", " ", "ira.png", 
  0, "Isabelle Chang", "Research assistant", "isc22@scarletmail.rutgers.edu", " ", "schwa.png", 
  0, "Katherine Taveras", "Research assistant", "kgtaveras@gmail.com", " ", "kat.png", 
  0, "Avery Field", "Research assistant", "", " ", "schwa.png", 
  0, "Jack Fastenau", "Research assistant", "", " ", "schwa.png", 
  0, "Kimberly Gómez", "Research assistant", "", " ", "schwa.png", 
  1, "John Thatcher", "Research assistant", "jet189@scarletmail.rutgers.edu", " ", "jt.png", 
  1, "Stephanie Rodríguez", "PhD student", "stephanie.rodrig@rutgers.edu", " ", "sr.png", 
  1, "Alexandria Minetti", "Research assistant", "amm850@scarletmail.rutgers.edu", " ", "am.png", 
  1, "Rhode-Taina Gardere", "Research assistant", "rgg62@scarletmail.rutgers.edu", " ", "rtg.png", 
  1, "Adrija Gadamsetty", "Research assistant", "ag1907@scarletmail.rutgers.edu", " ", "ag.png", 
  1, "Krishita Laungani", "Research assistant", "krl105@scarletmail.rutgers.edu", " ", "kl.png"
  ) |> 
  arrange(Role, Name)

current <- filter(members, current == 1)

cat('<div class="row">\n <div class="column">')
glue(
'
<div class="content">
 <div class="zoom">
 <center>
 <a href="{current$Website}">
 <img src="./images/members/{current$img}" alt="member" style="width:30%">
 </a>\n
 <small_text>[{current$Name}](mailto:{current$Email}), {current$Role}</small_text>\n
 </center>
 </div>
</div>
'
)
cat(' </div>\n</div>')
```






## Former members

```{r}
#| results: 'asis'
#| echo: false

members |> 
  filter(current == 0) |> 
  transmute(out = glue("- {Name} ({Role})")) |> 
  pull()

```


## Collaborators

- Dr. Miquel Simonet (Associate Professor, University of Arizona)
- Dr. Nicole Rodríguez (Post-doc, Adam Mickiewicz University, Poznań, Poland)
- Dr. Juan José Garrido Pozú (Assistant Professor, Furman University)




## Directory

```{r, members, echo=F, layout="l-body-outset"}
members |>
  select(-img, -current) |>
  arrange(Name) |>
  knitr::kable() |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive")
  )
```




<style type="text/css">

small_text {
  font-size: .85em;
}

* {
  box-sizing: border-box;
}

body {
  background-color: #fff;
}

.row {
  margin: 8px -16px;
}

/* Add padding BETWEEN each column (if you want) */
.row,
.row > .column {
  padding: 8px;
}

/* Create four equal columns that floats next to each other */
.column {
  float: left;
  width: 100%;
}

/* Clear floats after rows */ 
.row:after {
  content: "";
  display: table;
  clear: both;
}

/* Content */
.content {
  background-color: white;
  padding: 10px;
}

/* Responsive layout - makes a two column-layout instead of four columns */
@media screen and (max-width: 900px) {
  .column {
    width: 70%;
  }
}

/* Responsive layout - makes the two columns stack on top of each other instead of next to each other */
@media screen and (max-width: 600px) {
  .column {
    width: 90%;
  }
}

</style>

